Multi-modality Imagery Database for Plant Phenotyping

### 2015-04-29 datapaper_baseline.tex
xm's first edits

\begin{figure*}[t!]
\centering
\includegraphics[width=.98\textwidth]{Figures/overview}\\
\caption{Overview of the baseline method.}
\label{fig:methodOverview}
\end{figure*}

\section{Baseline Method and Performance}
\label{sec:baseline}
\subsection{Our framework}
We apply our automatic multi-leaf segmentation and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis fluorescence imagery to provide a baseline for future comparison.
Leaf segmentation aims at finding the correct number of leaves and the corresponding boundary of each leaf in each image.
Leaf alignment is to align the two tips of each leaf.
Leaf tracking is designed to track each leaf over time.

As shown in Fig~\ref{fig:methodOverview}, the input of this framework is a plant video and a set of predefined templates with various shapes, scales, and orientations.
To generate the template set, we first select $10$ templates with different aspect ratios from the labeled images in the training set together with the corresponding tip locations.
For each template, we scale it to $12$ different sizes in order to cover all size ranges in the database.
For each scale template, we rotated every $15^{\circ}$ to generate $24$ different directions.
Tip locations will be scaled and rotated accordingly.
Finally, we generate $2,880$ leaf templates.

%We also generate the two tips for each template for finding the corresponding tip points of each leaf via Chamfer Matching~\cite{barrow1977parametric}.
Our work is motivated by Chamfer Matching technique~\cite{barrow1977parametric}, which is used to align two edge maps.
We extend it to align multiple objects at the same time.
For each image, we use simple thresholding and edge detection to generate an edge map and mask.
First, we find the best location of each template in the edge map that has minimal chamfer matching distance, which will result in an over-complete set of leaf candidates.
Second, we apply multi-leaf alignment~\cite{yin2014a} approach to find an optimal set of leaf candidates on the last frame of the video, which will provide the information of the number of leaves, tip locations and boundaries of each leaf.
Third, we apply multi-leaf tracking~\cite{yin2014b} approach, which is based on leaf template transformation, to track leaves between continuous two frames.

In the tracking process, we develop a procedure to generate new leaves and delete small leaves.
For each frame of the video, we can generate a label image with each leaf being labeled with one color and the tip locations for each piece of leaf.
The label for each leaf in the video maintain the same during tracking process.

>>>>

\section{Baseline Method and Performance}
\label{sec:baseline}

To facilitate future research on this database, we provide a baseline approach and its performance by using the fluorescence modality.

\subsection{Multi-leaf segmentation and tracking framework}
We apply our automatic multi-leaf segmentation and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis fluorescence imagery to provide a baseline.
As shown in Figure~\ref{fig:methodOverview}, the input of this framework is a plant video and a set of predefined templates with various shapes, scales, and orientations.
To generate the template set, we first select $10$ templates with different aspect ratios from the labeled images in the training set together with the corresponding tip locations.
For each template, we scale it to $12$ different sizes in order to cover the entire range of leaf sizes in the database.
For each scale template, we rotate every $15^{\circ}$ to generate $24$ templates at different orientations.
Tip locations will be scaled and rotated accordingly.
Finally, we generate $2,880$ leaf templates.

%We also generate the two tips for each template for finding the corresponding tip points of each leaf via Chamfer Matching~\cite{barrow1977parametric}.
Our work is motivated by Chamfer Matching technique~\cite{barrow1977parametric}, which is used to align two edge maps.
We extend it to simultaneously align multiple overlapping objects.
For each image, we use simple thresholding and edge detection to generate an edge map and mask.
First, we find the best location of each template in the edge map that has the minimal Chamfer matching distance, which will result in an over-completed set of leaf candidates.
Second, we apply multi-leaf alignment~\cite{yin2014a} approach to find an optimal set of leaf candidates on the last frame of the video, which will provide the information of the number of leaves, tip locations and boundaries of each leaf.
Third, we apply multi-leaf tracking~\cite{yin2014b} approach, which is based on leaf template transformation, to track leaves between continuous two frames.

In the tracking process, we develop a procedure to generate new leaves and delete small leaves.
For each frame of the video, we can generate a label image with each leaf being labeled with one color and the tip locations for each estimated leaf.
The labeled color for each leaf in the video remains the same during the tracking process.

### 2015-04-29 datapaper_intro.tex
xm's first edits

\begin{table*}[t!]
	\centering
	\caption{Plant image databases, where the abbreviation in ``Applications'' column is defined as Leaf Classification (LC), Leaf Segmentation (LS), Leaf Counting (LO), Leaf Alignment (LA), and Leaf Tracking (LT).}
	%\resizebox{12cm}{!} {
	%\begin{tabular}{|l@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}
	\begin{tabular}{l|c|c|c|c|c|c}
		\hline
		\multirow{2}{*}{Database}&  \multirow{2}{*}{Modality}  & Appli-& Plant & Subject/ &Total  &  Labeled   \\ 						
			&         & cations &            Type         &       Classe \#         &  Image \#    & Image \# \\ \hline

Swedish leaf &  Scaned leaf & LC& Swedish trees & $15$ & $1,125$ & $1,125$ \\ \hline
Flavia& RGB  & LC& Leaves & $32$  & $2,120$ & $2,120$ \\ \hline
Leafsnap  & RGB & LC& USA trees & $184$ & $29,107$  &  $29,107$ \\ \hline
Crop/weed &  RGB &Weed detection & Crop/weed & $2$  & $60$ & $60$ \\ \hline
\multirow{2}{*}{LSC} & \multirow{2}{*}{RGB}  & \multirow{2}{*}{LS, LO} & Arabidopsis &  $43$ & $6287$ & $201$ \\ \cline{4-7}
							    &  & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
\multirow{2}{*}{MSU-PID}  & Fluorescence,  & LS, LO, & Arabidopsis &  $16$ &  $2304\times 4$ & $576\times 4$     \\ \cline{4-7}
							    & IR, RGB, Depth & LA, LT & Bean & $5$ & $350\times 4$  &  $175\times 4$ \\ \hline
	       \hline
	\end{tabular}
	%}
	\label{tab:database}
\end{table*}

@@

To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a new multi-modality plant imagery database collected at Michigan State University (MSU), termed ``MSU-PID''. The MSU-PID includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of imaging sensors, i.e., Fluorescence, infrared (IR), RGB color, and depth.
All four sensors are synchronized and are programmed to periodically capture imagery data for multiple consecutive days. Checkerboard-based camera calibration is performed between a pair of sensors, which results in the explicit correspondence between the pixels of {\it any} two modalities. 
For a subset of the database, we manually label the ground truth regarding the leaf identification number, locations of leaf tips and leaf segments. 
To provide a performance baseline for future research and comparison, we apply our automatic leaf segmentation framework~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the unique challenge of image analysis on this database.

>>>>

\begin{table*}[t!]
	\centering
	  \begin{threeparttable}
	\caption{Plant image databases.}
	%\resizebox{12cm}{!} {
	%\begin{tabular}{|l@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}
	\begin{tabular}{l|c|c|c|c|c|c}
		\hline
		\multirow{2}{*}{Database}&  \multirow{2}{*}{Modality}  &  \multirow{2}{*}{Applications}\tnote{a} & \multirow{2}{*}{Plant Type} & Subject/ &Total  &  Labeled   \\ 						
			&         &  &                    &       Classe \#         &  Image \#    & Image \# \\ \hline

Swedish leaf &  Scaned leaf & LC& Swedish trees & $15$ & $1,125$ & $1,125$ \\ \hline
Flavia& RGB  & LC& Leaves & $32$  & $2,120$ & $2,120$ \\ \hline
Leafsnap  & RGB & LC& USA trees & $184$ & $29,107$  &  $29,107$ \\ \hline
Crop/weed &  RGB &Weed detection & Crop/weed & $2$  & $60$ & $60$ \\ \hline
\multirow{2}{*}{LSC} & \multirow{2}{*}{RGB}  & \multirow{2}{*}{LS, LO} & Arabidopsis &  $43$ & $6287$ & $201$ \\ \cline{4-7}
							    &  & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
\multirow{2}{*}{MSU-PID}  & Fluorescence,  & LS, LO, & Arabidopsis &  $16$ &  $2304\times 4$ & $576\times 4$     \\ \cline{4-7}
							    & IR, RGB, Depth & LA, LT & Bean & $5$ & $350\times 4$  &  $175\times 4$ \\ \hline
	       \hline
	\end{tabular}
	%}
\begin{tablenotes}
	    \footnotesize	
            \item[a] The abbreviation in ``Applications'' column is defined as Leaf Classification (LC), Leaf Segmentation (LS), Leaf Counting (LO), Leaf Alignment (LA), and Leaf Tracking (LT).
        \end{tablenotes}
     \end{threeparttable}
	\label{tab:database}
\end{table*}

@@

To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a new multi-modality plant imagery database collected at Michigan State University (MSU), termed ``MSU-PID''. The MSU-PID includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of imaging sensors, i.e., Fluorescence, infrared (IR), RGB color, and depth.
All four sensors are synchronized and are programmed to periodically capture imagery data for multiple consecutive days. 
Checkerboard-based camera calibration is performed between a pair of sensors, which results in the explicit correspondence between the pixels of {\it any} two modalities.

The type and amount of manual labels on a datatbase is a critical enabler to the potential applications of the database.
For a subset of the MSU-PID database, we manually label the ground truth regarding the leaf identification number, locations of leaf tips and leaf segments. 
As a result,  MSU-PID is suitable for a number of applications, including 1) {\it leaf segmentation} that aims at estimating the correct segmentation mask of each leaf in an image, 2) {\it leaf counting} that estimates the correct number of leaves within a plant, 3) {\it leaf alignment} that aligns the two tips of each leaf -- the cornerstone of the leaf structure, and 4) {\it leaf tracking} that is designed to track each leaf over time.
Finally, to provide a performance baseline for future research and comparison, we apply our automatic leaf segmentation framework~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the unique challenge of image analysis on this database.
